Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-08-24 ms.tex
added a figure for my bosz model exploration.

\clearpage
\section{Conclusions}\label{sec:conclusions}

>>>>

\subsection{BOSZ Model Exploration}

We also convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M].

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/T_EFF_exploration.pdf}
\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/LOGG_exploration}
\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/MH_exploration.pdf}
\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/ALPHA_exploration.pdf}
\includegraphics[width=0.45\textwidth]{images/bosz_model_exploration/CM_exploration.pdf}
\caption{BOSZ parameter exploration.}\label{fig:boszModelParamsMedianSpec}
\end{centering}
\end{figure*}

\section{Conclusions}\label{sec:conclusions}
